\subsection{Liskov Substitution Principle}

\compareTable
{\acrlong*{lsp}}
{tab_convergence_lsp_principle_summarized}
{\addEvalRow{\conv & \noconv & \partconv & \noconv}}

\subsubsection{\acrlong*{soc}}

Adhering to \gls{lsp} in the software design leads to a more modular design and separation
of specific concerns. Therefore we state that \gls{lsp} converges with \gls{soc}.
\gls{lsp} states that objects of a derived class should be able to replace objects of the
base class without affecting the correctness of the program. This can only be achieved by
a strict separation of concerns in combination with Action version Transparent
implementations of the signature.

\subsubsection{\acrlong*{dvt}} 

\gls{lsp} has a limited alignment with the \gls{dvt} theorem. While \gls{lsp} focuses on
the substitutability of objects in class hierarchies, \gls{dvt} aims to handle changes in
data structures without impacting the system. By following \gls{lsp}, developers can
ensure that derived classes can be substituted for their base classes, which may help
reduce the impact of data structure changes on the system. However, \gls{lsp} does not
explicitly address data versioning and thus does not guarantee full convergence with
\gls{dvt}.

\subsubsection{\acrlong*{avt}}

The \gls{lsp} supports the \gls{avt} theorem. Both principles emphasize the importance of
allowing the extensibility of the system, without negatively impacting the desired
requirements. By adhering to \gls{lsp}, developers can create class hierarchies that can
be easily extended to accommodate new actions or changes in existing ones, which may
contribute to achieving \gls{avt}. However, adhering to \gls{lsp} alone may not guarantee
full convergence with \gls{avt}

\subsubsection{\acrlong*{sos}}

By designing class hierarchies according to \gls{lsp}, developers can create components
that are less prone to side effects caused by shared states. However, the alignment
between \gls{lsp} and \gls{sos} is very weak, and adhering to \gls{lsp} alone may not
guarantee full separation of states.
