\subsection{Open/Closed Principle}

\compareTable
{\acrlong*{ocp}}
{tab_convergence_ocp_principle_summarized}
{\addEvalRow{\conv & \partconv & \conv & \noconv}}

\subsubsection{\acrlong*{soc}}

The \gls{ocp} converges with the \gls{soc} theorem. \gls{ocp} states that software
implementations should be open for extension but closed for modification. When applying
\gls{ocp} correctly, modifications are separated from the original implementations. For
example by creating a new implementation of an interface or a base class. Conversely,
adhering to \gls{soc} does not guarantee the fulfillment of \gls{ocp}, as \gls{soc}
focuses on modularization and encapsulation, rather than the extensibility of modules.

\subsubsection{\acrlong*{dvt}}

The \gls{ocp} supports the \gls{dvt} theorem. While \gls{dvt} aims to handle changes in
data structures without impacting the system, \gls{ocp} focuses on the extensibility of
software entities. \gls{ocp} does not explicitly address data versioning, and thus does
not guarantee full convergence with \gls{dvt}. However, by designing modules that follow
\gls{ocp}, developers can create components that are more adaptable to changes in data
structures.

\subsubsection{\acrlong*{avt}}

The \gls{ocp} converges with the \gls{avt} theorem. Both principles emphasize the
importance of allowing changes or extensions to actions or operations without modifying
existing implementations. By adhering to \gls{ocp}, developers can create modules that can
be extended to accommodate new actions or changes in existing ones, effectively achieving
\gls{avt}.

\subsubsection{\acrlong*{sos}}

The \gls{ocp} has an indirect relationship with the Separation of States (SoSt) theorem.
However, not on a level where we can speak of convergence. \gls{sos} emphasizes isolating
different states within a system. Adhering to \gls{ocp} alone does not guarantee full
separation of states.
