\chapter{Conclusions and discussion} \label{chap_conclusions}

This thesis culminates a multifaceted exploration into the convergence of \gls{ca} with
\gls{ns}. We have drawn upon the author's firsthand experience in designing Software
Architectures used rigorous theoretical research and created a practical and working
Software Artifact. The primary objective was to investigate the convergence between \gls{ca}
and \gls{ns}, by analyzing their principles and design elements through theory and
practice. This Chapter will summarize the findings into a research conclusion.

\section{Conclusion}

A noteworthy distinction between \gls{ns} and \gls{ca} lies in their foundational roots.
\gls{ns} is a product of computer science research built upon formal theories and
principles derived from rigorous scientific investigation. Although, throughout this
thesis, \gls{ns} is referred to as a development approach, it is a part of Computer
Science.

Stability and evolvability are concepts not directly referenced in the literature of
\gls{ca}, but very much converges with the goal of \textcite[31]{mannaert_normalized_2016}.
Clearly depicted in Table \ref{tab_convergence_principles_summarized} The attentive reader
surely observes the shared emphasis on modularity and the separation of concerns, as all
SOLID principles have a stong convergence with \gls{soc}. Both approaches attempt to
achieve low coupling and high cohesion. In addition, \gls{ca} add the dimensions of
dependency management as usefull measure to improve maintainability and manage modularity.

The Transparency of Data versions appears to be underrepresented in the SOLID principles
of \gls{ca}. \gls{dvt} is primarily supported by the \gls{srp} of \gls{ca}, as evidenced
by the presence of ViewModels, RequestModels, ResponseModels, and Entities in the
Artifact. It is worth noting that these are an integral part of the design elements of
\gls{ca}. While \gls{ca} does address \gls{dvt} through the \gls{srp}, a more
comprehensive representation and integration of \gls{dvt} as a principle within the
principles of \gls{ca} will improve the convergence of \gls{ca} with \gls{ns}, potentially
improving the stability and evolvability of Software Systems based on \gls{ca}.

As indicated in Table \ref{tab_convergence_elements_summarized}, seems to lack a strong
foundation for receiving external triggers in it's desing phylosophy. This is partially
represented by the Controller element, however this element tends to be use for web
enabled environments like websites and Restful APIs. This may result in a less
comprehensive approach to receiving external triggers across various technologies or
systems.

A critical difference between \gls{ca} and \gls{ns} lies in their approach to handling
state. \gls{ca} does not explicitly address state management in its principles or design
elements. At the same time, \gls{ns} provides the principle of Separation of State,
ensuring that state changes within a Software System are stable and evolvable. This
principle can be crucial in developing scalable and high-performance systems, as it
isolates state changes from the rest of the system, reducing the impact of state-related
dependencies and side effects. 

The findings can only leads to the conclusion that the convergence between \gls{ca} and
\gls{ns} is incomplete because \gls{ca} needs specific state management principles. As a
result, \gls{ca} cannot fully ensure stable and evolvable software artifacts as defined by
\gls{ns}.


\section{Discussion}

In this research, the convergence between \gls{ca} and \gls{ns} has been thoroughly
investigated. While it has been demonstrated that the convergence between these two
approaches is not complete, the combination of both methodologies is highly beneficial for
a variety of reasons. The primary advantage of this convergence lies in the complementary
nature of \gls{ca} with \gls{ns}, where each approach provides strengths that can be
leveraged to address a strong architectural design. 

Clean Architecture offers a well-defined, practical, and modular structure for software
development. Its principles, such as SOLID, guide developers in creating maintainable,
testable, and scalable systems. This architectural design approach is highly suitable for
a wide range of applications and can be easily integrated with the theoretical foundations
provided by \gls{ns}. Conversely, the NS approach offers a more comprehensive theoretical
underpinning for evolvable systems, guiding achieving stability and evolvability.

Furthermore, the popularity and widespread adoption of Clean Architecture in the software
development community can be advantageous for Normalized Systems. As more developers
become familiar with CA and recognize its value to software design, incorporating \gls{ns}
principles becomes more accessible, leading to increased adoption and improved software
systems.

\input{chapters/conclusion/limits}
\input{chapters/conclusion/reflections}
