\subsection{Expanders} \label{subsec:expanders}

As described in section \ref{fi:plugin_architecture}, and portraited in figure
\ref{fi:plugin_architecture}, expanders are used as plugins by the Pantha Rhei expander
artifact. There are a couple of prerequisites applicable before the expander can be
dynamically loaded as a plugin at runtime.

\subsubsection*{Prerequisite 1: Project dependency}
The expander should have a dependency on the \gls{dll} of the project
\citecode{koks_pantharheigeneratordomain_2023}.

\subsubsection*{Prerequisite 2: Implements \code{koks_iexpanderinteractor_2023}} In order
to behave like an expander, one should behave like an expander. This is done by
implementing the \citecode{koks_iexpanderinteractor_2023} interface. Although not
required, it is strongly recommended to use the abstract
\citecode{koks_abstractexpander_2023} as it contains all the routines required
implementations of \citecode{koks_iexecutioninteractor_2023} like Harvesters,
Rejuvenators, Pre-, and PostProcessors.

\subsection*{Prerequisite 3: Implements
\code{koks_abstractexpanderdependencymanagerinteractor_2023}}
The Dependency Injection pattern is an interesting and beneficiary pattern that fully
adheres to the \gls{dip} principle. By implementing the abstract
\citecode{koks_abstractexpanderdependencymanagerinteractor_2023} all, for the expander
specific implementations of the following interfaces will automatically be registered and
made available for runtime processing.

\begin{itemize}
    \item The expander which should be an implementation of
    \citecode{koks_iexpanderinteractor_2023} or \citecode{koks_abstractexpander_2023}
    \item When applicable, the expander handers, which should be an implementation of \citecode{koks_iexpanderhandlerinteractor_2023}
    \item The default \citecode{koks_regionharvesterinteractor_2023} will automatically be
    executed during the generation process.
    \item Specific implementations of Harversters, which should be an implementation of \citecode{koks_iharvesterinteractor_2023} 
    \item The default \citecode{koks_regionrejuvenatorinteractor_2023} will automatically be
    executed during the generation process.
    \item Specific implementations of Rejuvenators, which should be an implementation of \citecode{koks_irejuvenatorinteractor_2023}
    \item The default PostProcessor \citecode{koks_installdotnettemplateinteractor_2023} will automatically be
    executed during the generation process.
    \item Specific implementation of PostProcessors, which should be an implementation of \citecode{koks_postprocessorinteractor_2023}
    \item The default PreProcessor \citecode{koks_uninstalldotnettemplateinteractor_2023} will automatically be
    executed during the generation process.
    \item Specific implementation of PreProcessors, which should be an implementation of \citecode{koks_preprocessorinteractor_2023}
\end{itemize}

