\subsection{The Controller Element} \label{converging_controller_element}

\evaluateElementTable{Controller}{tab_convergence_controller}{
    \addEvalRow{Data & \noconv & The Controllers and Data elements are not directly convergent, as
        the Controller element is focused on handling input/output from external systems, while Data
        elements represent domain objects.}

    \addEvalRow{Task & \noconv &  The Controllers and Task elements are not convergent. However,
        controllers might initiate Task elements when handling incoming requests.}

    \addEvalRow{Flow & \noconv &  The Controllers and Flow elements are not convergent, as
        the Controller element is focused on handling input/output from external systems,
        whilst the Flow element is concerned with the orchestration of Tasks.}

    \addEvalRow{Connector & \partconv & The Controller and Connector element are convergent to some
        degree. Both elements are involved in communication between components. The use of
        the Controller is a bit more strict it strictly defines communication from
        external parts of the systems, involving specific Interactor.}
    
    \addEvalRow{Trigger & \partconv & The Controller and the Trigger element of \gls{ns} are
        convergent to some degree as they both can initiate actions based on external
        events or requests. A Controller is primarily involved in receiving events or
        reqeusts from external sources, followed by the invocation of the appropriate
        interactor.}
}