\newacronym{ns}{NS}{Normalized Systems}
\newacronym{ca}{CA}{Clean Architecture}
\newacronym{oop}{OOP}{Object-Oriented Programming}
\newacronym{srp}{SRP}{Single Responsibility Principle}
\newacronym{ocp}{OCP}{Open/Closed Principle}
\newacronym{lsp}{LSP}{Liskov Substitution Principle}
\newacronym{isp}{ISP}{Interface Segregation Principle}
\newacronym{dip}{DIP}{Dependency Inversion Principle}
\newacronym{avt}{AvT}{Action Version Transparency}
\newacronym{dvt}{DvT}{Data Version Transparency}
\newacronym{soc}{SoC}{Separation Of Concerns}
\newacronym{sos}{SoS}{Separation of State}


\newglossaryentry{bibo}{ name={BIBO}, description={Bounded Input Bounded Output: A concept
used in Normalized Systems in combination with stability, derived from other scientific
fields } }

\newglossaryentry{erd}{
name={ERD},
description={Entity Relation Diagram: A visual representation of the relationships between entities in a database schema.}
}

\newglossaryentry{dll}{
name={DLL},
description={Dynamic Link Library: A file containing code and data that multiple programs can use simultaneously, allowing for code reuse and modular programming.}
}

\newglossaryentry{apa}{
name={APA},
description={American Psychological Association: A widely used citation style for academic writing, commonly used in social sciences.}
}

\newglossaryentry{vscode}{
name={VSCode},
description={Visual Studio Code: A popular source code editor developed by Microsoft, known for its versatility and extensive plugin ecosystem.}
}

\newglossaryentry{mdd}{
name={MDD},
description={Model Driven Development: An approach to software development that emphasizes the use of models and transformations to automatically generate code and other artifacts.}
}

\newglossaryentry{rep}{
name={REP},
description={The Reuse/Release Equivalence Principle: A principle in software engineering that states that components should be organized and released together if they are intended to be reused together.}
}

\newglossaryentry{ccp}{
name={CCP},
description={The Common Closure Principle: A principle in object-oriented design that states that classes that change together should be packaged together.}
}

\newglossaryentry{crp}{
name={CRP},
description={The Common Reuse Principle: A principle in object-oriented design that states that classes that are used together should be grouped together in a module or component.}
}

\newglossaryentry{cli}{
name={CLI},
description={Command Line Interface: A means of interacting with a computer program through text-based commands entered in a command-line interpreter.}
}

\newglossaryentry{mssql}{
name={MSSQL},
description={Microsoft SQL Database: A relational database management system developed by Microsoft, commonly used for storing and retrieving data in software applications.}
}

\newglossaryentry{ee}{
name={EE},
description={Enterprise Engineering: A discipline that focuses on the design and management of complex organizations and their information systems, taking a holistic approach to optimize their structure and operations.}
}

\newglossaryentry{solid}
{ name=SOLID, description={An acronym that stands for a set of design principles
    composed by \Citeauthor*{robert_c_martin_clean_2018}. The five
    principles that comprise SOLID are: \acrlong*{srp}, \acrlong*{ocp}, \acrlong*{lsp},
    \acrlong*{isp}, \acrlong*{dip}} }

\newglossaryentry{dto}
{ name=DTO, description={DTO stands for Data Transfer Object. It is a design pattern used
    in software development that involves simple objects for transferring data between
    layers or processes within an application. They are often lightweight, and have no
    business logic, serving primarily as a container for data to be transferred.} }

\newglossaryentry{nuget}
{ name=Nuget.org, description={NuGet is a free and open-source package manager for the
    Microsoft development platform, primarily targeting the .NET Framework. It unilizes
    third-party libraries into projects by providing a centralized platform for
    discovering, downloading, and managing dependencies.} }

    \newglossaryentry{crud}
{ name=CRUD, description={An acronym that stands for Create, Read, Update, and Delete. It
represents the basic operations required to manage persistent data in a database or
software system.} }