\subsection{Liskov Substitution Principle}

\evaluatePrincipleTable{\gls{lsp}}{table_lsp_convergence}{ 
    
\addEvalRow{\gls{soc} & \fullConvergence & \gls{lsp} states that objects of a derived
class should be able to replace objects of the base class without affecting the program
negatively. Replacing objects can only be achieved by separating them and converging the
principles inherently. A good example is the implementation of the
\citecode{koks_itemplateinteractor_2023}, where the template engine Scriban
\parencite{github_scriban_2023} is used to generate code instantiations as a result of the
Expanding the model \parencite{koks_scribantemplateinteractor_2023}. We could easily
replace the Scriban template engine with another engine, only impacting the Dependency
Injection Register.}
    
\addEvalRow{\gls{dvt} & \noConvergence & The convergence between \gls{lsp} and \gls{dvt} is weak,
and no manifestations are found in the artifacts.}
    
\addEvalRow{\gls{avt} & \npartialConvergence & The \gls{lsp} supports the \gls{avt} principle.
Both principles emphasize the importance of allowing the extensibility of the software
system. By adhering to \gls{lsp}, the architecture allows for class hierarchies that can
be easily extended to accommodate new (versions of) actions, which can contribute to
achieving \gls{avt}. However, adhering to \gls{lsp} alone may not guarantee full adherence
to \gls{avt}. Consider \citecode{koks_icreategateway_2023} in Code Listing
\ref{list_ICreateGatewayExamples}. The artifact contains multiple implementations of this
interface. Each implementation could be considered a different version applied to the
interface.} 
    
\addEvalRow{\gls{sos} & \noConvergence & The \gls{lsp} does not relate to the \gls{sos}
principle. The convergence of both principles is weak, and no manifestations are found in
the artifacts.} }
