\subsection{Open/Closed Principle}

\evaluatePrincipleTable{\gls{ocp}}{table_ocp_alignment}{ 
    
\addEvalRow{\gls{soc} & \fullAlignment & The \gls{ocp} is strongly aligned with the \gls{soc}
    principle of \gls{ns}. \gls{ocp} states that software architectures should be open for
    extension but closed for modification. When applying \gls{ocp} correctly, the
    architecture supports new requirements built as an extension, affecting as few
    existing implementations as possible. Conversely, adhering to \gls{soc} does not
    guarantee the adherence of \gls{ocp}, as \gls{soc} focuses on modularization and
    encapsulation rather than the extensibility of functionality. The same example with
    the Tasks provided in sub-section \ref{srp} is also an excellent manifestation of this
    principle.} 
    
\addEvalRow{\gls{dvt} & \partialAlignment & While \gls{dvt} aims to handle changes in data
    structures without impacting the system, \gls{ocp} focuses on the extensibility of
    software architectures. Although \gls{ocp} does not explicitly address data version
    transparency, \gls{ocp} promotes architectures that are more adaptable to changes in
    data structures. Separating \glspl{dto} specific for a use case is a great example and
    manifestation in the Artifact
    \parencite{koks_requestmodels_2023,koks_viewmodels_2023}. However, there is no
    complete alignment because the use of \gls{ocp} does not guarantee \gls{dvt}.}
    
\addEvalRow{\gls{avt} & \fullAlignment &The \gls{ocp} is strongly aligned with the \gls{avt}
    principle of \gls{ns}, as both principles emphasize the importance of allowing changes
    or extensions to actions without affecting existing implementations. \gls{ocp} is also
    closely related to \gls{srp}. Besides \gls{srp}, \gls{ocp} have the most
    manifestations in the Artifact, some of which are already mentioned in previous
    examples. } 
    
\addEvalRow{\gls{sos} & \noAlignment & The \gls{ocp} indirectly relates to the \gls{sos}
    principle. The alignment of both principles is weak, and no
    manifestations are found in the artifacts. } 
}