\subsection{Component architecture} \label{subsec_layers}

\gls{ca} organizes their components into distinct layers, each with responsibilities. This
structure promotes the separation of concerns, maintainability, testability, and
adaptability. The following section is a short description of each layer
\parencite{robert_c_martin_clean_2018}.

\subsubsection{Domain layer}
This layer contains the application's core business objects, rules, and domain logic. Entities
represent the fundamental concepts and relationships in the problem domain and are indepen-
dent of any specific technology or framework. The domain layer focuses on encapsulating the
essential complexity of the system and should be kept as pure as possible.

\subsubsection{Application layer}
This layer contains the use cases or application-specific business rules orchestrating the
interaction between entities and external systems. Use cases define the application's
behavior regarding the actions users can perform and the expected outcomes. This layer is
responsible for coordinating the flow of data between the domain layer and the
presentation or infrastructure layers while remaining agnostic to the specifics of the
user interface or external dependencies.

\subsubsection{Presentation layer}
This layer translates data and interactions between the use cases and external actors,
such as users or external systems. Interface adapters include controllers, view models,
presenters, and data mappers, which handle user input, format data for display, and
convert data between internal and external representations. The presentation layer should
be as thin as possible, focusing on the mechanics of user interaction and deferring
application logic to the use cases.

\subsubsection{Infrastructure layer}
This layer contains the technical implementations of external systems and dependencies,
such as databases, web services, file systems, or third-party libraries. The
infrastructure layer provides concrete implementations of the interfaces and abstractions
defined in the other layers, allowing the core application to remain decoupled from
specific technologies or frameworks. This layer is also responsible for configuration or
initialization code to set up the system's runtime environment.

By organizing code into these layers and adhering to the principles of \gls{ca},
developers can create software systems that are more flexible, maintainable, and testable,
with well-defined boundaries and separation of concerns