\addcontentsline{toc}{chapter}{Acknowledgements} % Add Table of Contents to the Table of Confents
\chapter*{Acknowledgements}
\small

\begin{center}
\enquote{\textit{With unwavering commitment, heartfelt encouragement, \\and steadfast support, the
impossible becomes possible.}}
\end{center}

Looking back, I never imagined I would embark on this academic journey. As a youngling, I
struggled with a focusing disorder, which led me to attend a school specializing in
helping kids with similar challenges. Despite this, I discovered I could excel by
dedicating myself to enjoyable activities. Early in my life, this manifested primarily in
sports.

I knew I had to provide for myself as an adult, so I pursued an education in what I loved
most: Sports. Consequently, the first decade of my professional career revolved around
being a sports instructor. Eventually, my interests shifted toward the technical
challenges of software programming. I decided to take the plunge and pursue it
professionally. So, I embarked on my first educational endeavor, my bachelor's degree in
Computer Science, completed in 2012. In hindsight, it was the best decision I have made.
It caused a giant leap forward from a career perspective but also for my personal growth.
My decision has brought me to this point where I am close to completing my Master's
degree, which makes me incredibly proud. 

It would have been a much more difficult journey without the encouragement and support of
many people. Rene Bliekendaal encouraged and convinced me to embark on this journey. Thank
you! I also greatly respect my employer for facilitating this pursuit while I continued to work
full-time. Your flexibility has played an important role in making it a reality.

I sincerely thank my supervisor, Hans Mulder, and promoter, Geert Haerens, for their
invaluable guidance, feedback, and mentorship throughout my research. Your expertise and
insights have been instrumental in shaping my work and ensuring this success. Also, a
special mention goes to Frans Vertreken, who really stepped up in guiding me in the early
stages of research when no one else was available. Your knowledge and encouragement have
been inspiring and laid the basis for my result.

I extend my heartfelt gratitude to Antwerp Management School, which provided me with an
excellent platform to pursue my personal and scholarly growth. To everyone else who has
played a role in this journey, no matter how big or small, I offer my heartfelt thanks.
This achievement would not have been possible without each one of you.

So, what is next for me? First, I fully intend to repay my employer's continued support
and encouragement by sharing my knowledge and planning to bring additional value. Then, in
my free time, I'll spend some well-deserved and needed time focusing on my health and my
closest family members. After that? I'm not sure yet, but I want to explore more on the
subject of Software stability and Evolvability, as this is where my true passion and
potential lie. 

\noindent --- Gerco