\chapter{Installing \& using Pantha Rhei} \label{appendix_installation_instructions} 

\section{Installation instructions} \label{appendix_installation_prerequisits}
\subsection*{Step 1: Create output folder}
Create an output folder so that the applications...
\begin{itemize}
    \item ...has a location where to find the required expanders.
    \item ...has a location where the log files are stored.
    \item ...has a location where the result of the generation processes can be stored.
\end{itemize}

The location of the output folder is irrelevant.

\subsection*{Step 2: Create the Nuget configuration file}
Add a configuration file named \emph{nuget.config} file to the output folder with the
the following content: 

\lstinputlisting[ caption={The content of the Nuget configuration file},
label={list_nugetconfig}] {Snippets/nuget.config}

This config file is needed for the following step where the Pantha Rhei application is
installed. The file contains the information to the private feed where the Pantha Rhei
application can be downloaded and installed.

\subsection*{Step 3: Installing Pantha Rhei} \label{appendix_installing_pantha_rhei} 
Open a console in on the location where the Nuget configuration file is stored. The
following command will download the package, and start the installation process which is
executed in the background. 

\lstinputlisting[
    caption={The install command},
    label={appendix_list_install-command}]
    {Snippets/dotnet-install-command.txt}

\subsection*{Step 4: Download \& Install the Expanders}
By clicking on the following link, an archived folder will be presented as a download by
your browser. Download the archived folder and extract it on completion. Store the
extracted folder, in a subfolder called \emph{Expanders} in the root of the output
folder. By doing so, the following folder structure should be available:

\begin{forest}
    for tree={
      font=\ttfamily,
      grow'=0,
      child anchor=west,
      parent anchor=south,
      anchor=west,
      calign=first,
      inner xsep=7pt,
      edge path={
        \noexpand\path [draw, \forestoption{edge}]
        (!u.south west) +(7.5pt,0) |- (.child anchor) pic {folder} \forestoption{edge label};
      },
      % style for your file node 
      file/.style={edge path={\noexpand\path [draw, \forestoption{edge}]
        (!u.south west) +(7.5pt,0) |- (.child anchor) \forestoption{edge label};},
        inner xsep=2pt,font=\small\ttfamily
                   },
      before typesetting nodes={
        if n=1
          {insert before={[,phantom]}}
          {}
      },
      fit=band,
      before computing xy={l=15pt},
    }  
    [PanthaRhei.Output
    [Expanders
        [.Templates]
    ]
    [nuget.config, file]
  ]
\end{forest}

The Pantha Rhei application is now ready for use.

\subsection*{Step 5: Setup a SQL database}
Currently, Pantha Rhei is working with an MS SQL database for storing the model of the
applications. Set up a SQL Database. This can either be a licensed version of SQL Server,
the free-to-use SQL Express or an Azure SQL instance. See
\url{https://www.microsoft.com/en/sql-server/sql-server-downloads} for more information.
Make sure to have a valid connection string to the SQL server instance that is needed in
step \fullref{appendix_run_flux}.
