\subsection{The Controller Element} \label{converging_controller_element}

\evaluateElementTable{Controller}{tab_convergence_controller}{ \addEvalRow{Data &
    \noConvergence & There is no convergence between the Controller element of \gls{ca} and
    the Data element of \gls{ns} and no manifestations are found in the Artifact.}

    \addEvalRow{Task & \noConvergence &  There is no convergence between the Controller
    element of \gls{ca} and the Task element of \gls{ns} and no manifestations are found
    in the Artifact.}

    \addEvalRow{Flow & \noConvergence &  There is no convergence between the Controller
    element of \gls{ca} and the Flow element of \gls{ns} and no manifestations are found
    in the Artifact.}

    \addEvalRow{Connector & \npartialConvergence & Although the Controller of \gls{ca}
    supports the intent of the Connector element of \gls{ns}, they are only partially
    interchangeable. While both elements are involved in the interaction between
    components, the Controller element from \gls{ca} primarily intends to interact with
    external systems using a specific protocol or technology involving user or web
    interfaces. An example of such a Controller is illustrated in Code Listing
    \ref{list_entitycontroller}. \parencite{koks_entitycontroller_2023}. In this example,
    the Controller exposes a Restful interface.}
    
    \addEvalRow{Trigger & \npartialConvergence & Although the Controller of \gls{ca} supports
    the intent of the Trigger element of \gls{ns}, they are only partially interchangeable.
    While both elements are involved in receiving events from external systems, a Controller
    is also able to initiate communication with the same external systems using specific
    protocols or technologies involving user or web interfaces. } }