\subsection{Expander Framework \& Clean Architecture Expander Requirements} \label{expander_framework_requirements}

In addition to the more generic requirements of previous sections, the following
requirements are specific for Clean Architecture Exander \& Expander Framework artifact.

\requirement{Expander Framework}{table_requirements_expanderframework}{
    \addEvalRow{The Expander Framework enables interaction with the Clean Architecture Expander via a
    \gls{cli}. The \gls{cli} is implemented in the Presentation layer of the
    Expander Framework.}

    \addEvalRow{The Expander Framework retrieves the model from an \gls{mssql} using the
    EntityFramework ORM technology. The EntityFramework technology is implemented in the
    Infrastructure layer of the Expander Framework.}

    \addEvalRow{The Expander Framework loads and executes the configured Expanders. In the case of
    this research, only the Clean Architecture Expander is applied.}

    \addEvalRow{The Expander Framework supports generic harvesting and injection, which can be
    used or extended by the Expanders using the \gls{ocp} principle.}

    \addEvalRow{The Expander Framework supports generic template handling, which can be used or
    extended by the Expanders using the \gls{ocp} principle. }

    \addEvalRow{The Expander framework adheres to this chapter's component and software Requirements
    specified in Sections \ref{component_requirements} and \ref{software_requirements}.}
}

\requirement{The Clean Architecture Expander}{table_requirements_expander}{
    \addEvalRow{The Clean Architecture Expander generates a C\# net7.0 RESTful service that provides an
    HTTP interface on top of the meta-model of the Expander Framework, allowing the basic
    \gls{crud} operations.}

    \addEvalRow{The Clean Architecture Expander consists solely of an Application layer and reuses
    the Domain layer of the Expander Framework.}

    \addEvalRow{The Clean Architecture Expander adheres to this chapter's component and software
    Requirements specified in Sections \ref{component_requirements} and
    \ref{software_requirements}.}
}