\section{Research requirements} \label{sec:research_requirements} 

In order to address \nameref{rq1} and \nameref{rq2} we outlined in Chapter
\ref{sec:research_questions}, we need to know what violations in the context of \gls{ns}
can occur in a software artifact. In chapters \ref{sec:ns_theory} we have shown that
\gls{ns} attempts to achieve evolvability by achieving stability. Through the extensive
and consistent use of the \gls{ns} theorems, a modular design emerges that is free of
instabilities. Or in terms used by the \gls{ns} theorem: the absence of combinatorial
effects. However, as described in section \ref{sec:artifact_requirements}, the artifacts
are designed based on the principles and philosophy of \gls{ca}. The \gls{ns} theorems are
not considered using the design phase of the artifacts. 

To be able to analyze the stability of the artifacts the following functional requirement
specifications are reused \parencite[254-259]{mannaert_normalized_2016}. They are noted
without the mathematical formulas that are present in cited sources.


\mycolorbox{An information system needs to be able to represent instances of data
entities. A data entity consists of a number of data fields. Such a field may be a basic
data field representing a value of a reference to another data entity.}
{Research Requirement 1}

\mycolorbox{An information system needs to be able to execute processing actions on
instances of data entities. A processing action consists of a number of consecutive
processing tasks. Such a task may be a basic task, i.e., a unit of processing that can
change independently, or an invocation of another processing action.}
{Research Requirement 2}

\mycolorbox{An information system needs to be able to input or output values of instances of data entities through connectors.}
{Research Requirement 3}

\mycolorbox{An existing information system representing a set of data entities, needs
to be able to represent: 
\begin{itemize}
    \item a new version of a data entity Dm that corresponds to including an additional
    data field
    \item an additional data entity 
\end{itemize}}
{Research Requirement 4}

\mycolorbox{An existing information system providing a set of processing actions,
needs to be able to provide:
\begin{itemize}
    \item a new version of a processing task, whose use may be mandatory
    \item a new version of a processing action, whose use may be mandatory
    \item an additional processing task
    \item an additional processing action
\end{itemize}}
{Research Requirement 5}