\chapter{Evaluation results} \label{chap_evaluation}

This Chapter focuses on the comparison of \gls{ca} and \gls{ns} and explores the
convergence between the two architectural design approaches. We will start by comparing
the principles of \gls{ca} with the theories of \gls{ns} and analyze how they converge in
their approach and the effect on the software design. In section
\ref{sec_converging_elements}, we will compare the design elements of the two
architectural approaches. We will highlight the similarities and differences in their
implementation, in order to determine the further convergence of the two discussed
architectural design approaches.

To conduct this comparison, we used a combination of artifacts and a literature study. We
analyzed real-world examples of software artifacts that were designed using \gls{ca}, and
reviewed the relevant literature to gain a comprehensive understanding of both approaches.

Throughout this evaluation chapter, we will explore the strengths and weaknesses of each
approach, as well as the potential benefits of their convergence. By examining the
principles and design elements of \gls{ca} and \gls{ns}, we hope to provide a clear
understanding of the effects of using the different approaches in conjunction with each
other.

\input{Chapters/Evaluation/Principles/ConvergenceOfPrinciples.tex}
\input{Chapters/Evaluation/Principles/SRP.tex}
\input{Chapters/Evaluation/Principles/OCP.tex}
\input{Chapters/Evaluation/Principles/LSP.tex}
\input{Chapters/Evaluation/Principles/ISP.tex}
\input{Chapters/Evaluation/Principles/DIP.tex}


\input{Chapters/Evaluation/Elements/ConvergenceOfElements.tex}
\input{Chapters/Evaluation/Elements/Entity.tex}
\input{Chapters/Evaluation/Elements/Interactor.tex}
\input{Chapters/Evaluation/Elements/RequestModel.tex}
\input{Chapters/Evaluation/Elements/ResponseModel.tex}
\input{Chapters/Evaluation/Elements/ViewModel.tex}
\input{Chapters/Evaluation/Elements/Controller.tex}
\input{Chapters/Evaluation/Elements/Gateway.tex}
\input{Chapters/Evaluation/Elements/Presenter.tex}
\input{Chapters/Evaluation/Elements/Boundary.tex}


